		% TODO: Short introduction

\subsection{Components}
The grid computing platform consists of a single central server that manages
data to be computed, and a number of clients that do the actual computations.
The server is written in Scala in an object-oriented fashion, making use of
functional language features wherever possible and feasible. The client is
written in Javascript (and some HTML), and runs in the browser. The server will
push job-specific code (in Javascript) and data (in JSON) to the client.

In addition to the generic client, there is also a specialized client
implementation of the wordcount job written in Scala. This client does not
interpret the code received from the server, but merely checks it to confirm
that it is a wordcount job.
	
	\subsection{How does it work?}
		The server contains a list of jobs. To request a map or reduce job, a client can navigate to /jobs. 
		This call returns an id for the current job, that the client can execute. Using this id, 
		the client can request the javascript code for the job with the corresponding id by calling /\{id\}/code
		and the input data for the job with the corresponding id by calling /\{id\}/input.
		The code for the job should contain a call to the fetch function to request data and should contain a call to the push
		function to send the result back to the server.
		Data can be send to the server by calling /\{id\}/output.
		
		In this way, the framework is very generic meaning that a variety of MapReduce algorithms can be run on the platform.
		
		The browser client starts to check for pending tasks when the start button is clicked and stops when the stop button is clicked.
		When the stop button is clicked while executing a job, it will continue until the job is finished.